A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-05-21 2022/Sensors/kNN.tex
translate last comment

%%% ДЛЯ РУССКОГО ТЕКСТА закомментировать потом!
\usepackage{inputenc}
\usepackage[T2A,T1]{fontenc}
\usepackage[english,russian]{babel}
\usepackage{cmap}
%%%

@@

%Штанюк
\item
\textcolor[rgb]{1,0,0}{\textbf{DS-WISDM} -- a dataset of dimension 3, representing data from Smartphone and Smartwatch Activity and Biometrics Dataset Data Set \cite{ds-3}.}

@@

%Штанюк
\textcolor[rgb]{1,0,0}{Представляет интерес изучение зависимости времени поиска ближайших соседей от их числа при большом количестве объектов. Для такого исследования был выбран датасет DS-WISDM \cite{ds-3}. The raw accelerometer and gyroscope sensor data is collected from the smartphone and smartwatch at a rate of 20Hz. It is collected from 51 test subjects as they perform 18 activities for 3 minutes apiece. Традиционное использование этого датасета предполагает обработку raw data, которая включает разбиение данных на блоки фиксированного размера и вычисление статистических характеристик для каждого блока. В дальнейшем, каждый блок рассматривается в качестве самостоятельного объекта с набором присущих ему характеристик, определяющих активность субъекта за рассматриваемый временной промежуток. При этом число блоков будет существенно меньше исходного числа объектов. В рамках нашего исследования для сохранения большого числа объектов в датасете мы не стали использовать этот традиционный подход и работали с необработанными данными. Для определения ближайших соседей использовались только пространственные координаты, без привязки ко времени. Перед проведением вычислительного эксперимента из исходного датасета были удалены встречающиеся дубликаты. В получившемся наборе осталось порядка 7 млн. объектов, относящихся к 18 классам. На рисунке \label{figW} приведены результаты  поиска ближайших соседей в этом дататесе. Из двух процедур нахождения соседей была оставлена kNN-ME(A) как более эффективная по сравнению с kNN-ME(B); использовалось число evolvents L = 8. Как и в предыдущих экспериментах, результаты показывают, что при числе соседей K<100 процедура kNN-ME(A) также работает быстрее, чем kNN-KD.}

%Штанюк
\begin{figure}
\widefigure
\includegraphics[width=0.5\linewidth]{figW.pdf}
\caption{Running times of the algorithms with $N = 3$, 7 million objects\label{figW}}
\end{figure}

%Сысоев
\textcolor[rgb]{1,0,0}{Представленные выше результаты экспериментов показывают, что даже при числе сэмплов в несколько миллионов времена работы рассмотриваемых в статье алгоритмов отстаются небольшими (в пределах миллисекунды). Таким образом, вопросы распараллеливания и реализации многопоточных версий разработанных алгоритмов в статье не рассматриваются.}

>>>>

%%% ДЛЯ РУССКОГО ТЕКСТА закомментировать потом!
%\usepackage{inputenc}
%\usepackage[T2A,T1]{fontenc}
%\usepackage[english,russian]{babel}
%\usepackage{cmap}
%%%

@@

%Штанюк
\item
\textcolor[rgb]{1,0,0}{\textbf{DS-WISDM} -- a dataset of dimension 3, representing accelerometer and gyroscope time-series sensor data collected from a smartphone and a smartwatch \cite{ds-3}.}

@@

%Штанюк
\textcolor[rgb]{1,0,0}{It is of interest to study the dependence of the nearest-neighbour search time on the number of such neighbours in the case of a large number of objects.  For this study, we chose the DS-WISDM dataset \cite{ds-3}. The raw accelerometer and gyroscope sensor data is collected from the smartphone and smartwatch at a rate of 20Hz. It is collected from 51 test subjects as they perform 18 activities for 3 minutes apiece. The raw accelerometer and gyroscope sensor data is collected from a smartphone and a smartwatch at a rate of 20Hz. It is collected from 51 test subjects as they perform 18 activities for 3 minutes apiece. Traditional use of this dataset involves raw data processing, which includes splitting the data into blocks of fixed size and calculating statistical characteristics for each block. Subsequently, each block is treated as an independent object with a set of inherent characteristics determining the subject's activity during a given time interval.  After such processing, the number of blocks will be substantially smaller than the original number of objects.}

\textcolor[rgb]{1,0,0}{In our study, in order to keep a large number of objects in the dataset, we did not use this traditional approach and worked with raw data. Only spatial coordinates, with no time reference, were used to determine the nearest neighbours. Before conducting the computational experiment, we removed the duplicates found in the original dataset. After that, about 7 million objects belonging to 18 classes remained in the resulting set.  Figure \ref{figW} shows the results of the nearest neighbour search in this dataset. Of our two neighbour finding procedures, kNN-ME(A) was retained as a more efficient one compared to kNN-ME(B); the number of evolvents $L = 8$ was used in this case. Similar to previous experiments, the results show that when the number of neighbours $K$ is less than $100$, the kNN-ME(A) procedure is also faster compared to the kNN-KD method.}

%Штанюк
\begin{figure}
\widefigure
\includegraphics[width=0.5\linewidth]{figW.pdf}
\caption{\textcolor[rgb]{1,0,0}{Running times of the algorithms with $N = 3$, 7 million objects}\label{figW}}
\end{figure}

%Сысоев
\textcolor[rgb]{1,0,0}{The experimental results presented above show that even with the number of objects in millions the running times of the algorithms considered in the paper remain small (within milliseconds). Therefore, the issues of parallelizing and implementing multi-threaded versions of the developed algorithms have not been considered in this paper.}
